Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-06 SupportingInformation.Rmd
adding beta variation chunk for asym sensitivity analysis and some minor changes

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

@@

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

@@

```{r cause4copula_stat, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

@@

<!--Another model, distinct from the above, Dan and Shya to discuss-->

>>>>

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

@@

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

@@

```{r cause4copula_stat, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

@@

<!--Another model, distinct from the above, Dan and Shya to discuss-->
```{r asym_sens_beta_variation, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)
source("asym_sensitivity.R")

#-----------------------------------------------------------------------------------
# This function takes 
# Input :
#       N : number of global and local noise points you want
#       rho : covariance of global noise matrix
#       alpha : a number : local noise coeeficient
#       beta : growth factor of pop
#       decrease : logical (controls the nature of global noise)
#       numkeep_last : number of points you want to keep for the pop matrix from the end
#       ploton : logical for optional plot

# Output :
#     a list of 4 pop matrices 
#                         1. (for beta=+ve, decrease=F)
#                         2. (for beta=+ve, decrease=T)
#                         3. (for beta=-ve, decrease=F)
#                         4. (for beta=-ve, decrease=T)

plotter_asym_sens_beta_varn<-function(N,rho,alpha,beta,numkeep_last,ploton){

  pop<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  neg_beta<- -beta
  pop_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  if(ploton==T){
    op<-par(mfrow=c(2,2),mar=c(4,3,1.5,1),mgp=c(2,1,0))

    plot(pop[,1],pop[,2],col="red",main = bquote(beta ==.(beta)))
    mtext(paste0("(A)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_d[,1],pop_d[,2],col="blue",main = bquote(beta ==.(beta)))
    mtext(paste0("(B)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_neg_beta[,1],pop_neg_beta[,2],col="orange",main = bquote(beta ==.(neg_beta)))
    mtext(paste0("(C)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_d_neg_beta[,1],pop_d_neg_beta[,2],col="skyblue",main = bquote(beta ==.(neg_beta)))
    mtext(paste0("(D)"),side = 3, line=0.3, adj=0.3, col="black")

    par(op)
  }

  return(list(pop=pop,
              pop_d=pop_d,
              pop_neg_beta=pop_neg_beta,
              pop_d_neg_beta=pop_d_neg_beta))

}
#--------------------------------------------------------------
N<-10000
rho<-0.8
alpha<-0.2
numkeep_last<-1000

pdf("./Results/asym_sens_results/beta_0.1_asym_sen.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

pdf("./Results/asym_sens_results/beta_0.9_asym_sens.pdf")
ans_beta_0.9<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.9,numkeep_last=numkeep_last,ploton=T)
dev.off()

vlist_beta_0.1_beta_0.9<-c(ans_beta_0.1,ans_beta_0.9) # a list of 8 matrices

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AIC_w","relLTdep_AICw","relUTdep_AIC_w","p_CvM","p_KS","Numboot_success")
bg <- intToUtf8(0x03B2) 
cname<-paste0(bg, c("_0.1","_0.1_decrease_T","_-0.1","_-0.1_decrease_T","_0.9","_0.9_decrease_T","_-0.9","_-0.9_decrease_T"))
colnames(summary_stat)<-cname

stat_npa_asym_beta_0.1_beta_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible beta variation

for(ic in c(1:8)){
  v<-vlist_beta_0.1_beta_0.9[[ic]]
  res<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=c(1,3:10,13:14,16:20),level=0.05,
                      AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                      gofnormal=F,status=F)

  summary_stat[1,ic]<-max(res$InfCritRes$AICw)
  summary_stat[2,ic]<-res$InfCritRes$AICw[1]
  summary_stat[3,ic]<-res$relLTdep_AICw
  summary_stat[4,ic]<-res$relUTdep_AICw
  summary_stat[5,ic]<-res$GofRes_CvM
  summary_stat[6,ic]<-res$GofRes_KS
  summary_stat[7,ic]<-res$Numboot_success

  stat_npa_asym_beta_0.1_beta_0.9[[ic]]<-bivfunctionplot(v=v,resloc="./Results/asym_sens_results/",nametag=cname[ic],numbin=10)

}

saveRDS(summary_stat,"./Results/asym_sens_results/beta_variation_summary_stat.RDS")
saveRDS(stat_npa_asym_beta_0.1_beta_0.9,"./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")
```
